### 2016-07-06 store-consistency.tex
He Zhu's qn addressed.
Edits.

We now consider the proof of the example in Fig.~\ref{fig:motiv-eg-1}
in greater detail. Both withdraw transactions are run at {\sc si}
isolation, hence $\I_c$ is $\lambda\E.~\underE{\C{SI(Wd1)}} \conj
\underE{\C{SI(Wd1)}}$. We assume an {\sc sc} store, such as a
conventional RDBMS, whose store-specific trace invariant ($\I_s$) is
the maximul visibility weakening (Def.~\ref{def:maxvis}) of {\sc sc}
w.r.t. $\I_c$, as described in \S\ref{sec:store-consistency}. In
concrete terms, this means that an effect added to $\E.\A$ by the
current thread or a concurrent thread immediately becomes visible to
the subsequent operations unless we produce a witness that such
visibility violates $\I_c$. As usual, $\I$ is $\I_s \conj \I_c$. Note
that the language of our specifications and (most of) the assertions
on executions is a decidable subset of the first-order logic (in
particular, our specifications and rely-guarantee rules are carefully
crafted to avoid transitive closures and quantification over infinite
domains). Consequently, the proof obligations generated by the
application of our rules can often be discharged via an SMT solver. We
nonetheless give full details in the following.

@@

\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{B} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{B=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{B=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{B=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}
For the sake of completeness, we also explicitly represent the fact
that all the effects added by $R_1$ are of \C{Wd2}. This is needed to
prove that an interference from \C{Wd2} does not affect the local
state of \C{Wd1}.

>>>>

We now consider the proof of the example in Fig.~\ref{fig:motiv-eg-1}
in greater detail. Both withdraw transactions are run at {\sc si}
isolation, hence $\I_c$ is $\lambda\E.~\underE{\C{SI(Wd1)}} \conj
\underE{\C{SI(Wd2)}}$. We assume an {\sc sc} store, such as a
conventional RDBMS, whose store-specific trace invariant ($\I_s$) is
the maximul visibility weakening (Def.~\ref{def:maxvis}) of {\sc sc}
w.r.t. $\I_c$, as described in \S\ref{sec:store-consistency}. In
concrete terms, this means that an effect added to $\E.\A$ by the
current thread or a concurrent thread immediately becomes visible to
the subsequent operations unless we produce a witness that such
visibility violates $\I_c$. As usual, $\I$ is $\I_s \conj \I_c$. Note
that the language of our specifications is a decidable subset of the
first-order logic. In particular, our specifications and
rely-guarantee rules are carefully crafted to avoid transitive
closures and quantification over infinite domains. The domain of
assertions is often linear arithmetic, which is also decidable.
Consequently, the proof obligations generated by the application of
our rules can often be discharged via an SMT solver. We nonetheless
give full details in the following.

@@

\begin{smathpar}
\begin{array}{lcl}
  R_1 & = & \{ (\E,\E') \;|\; \neg\underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \neg\underE{\committed(\C{Wd2})} \conj \I(\E) \conj \I(\E')\\
%       \conj (\E'-\E) \subseteq \C{Wd2} \conj \\
%   & & \hspace*{0.5in} \E' \Vdash \committed(\C{Wd2}) ~\Rightarrow~ \E'
%       \Vdash \C{Wd2} \wrstoar \C{B} \conj \\ 
%   & & \hspace*{0.5in} \underE{\committed(\C{Wd1})} \conj \E' \Vdash
%   \committed(\C{Wd2}) \Rightarrow \C{B=k-a1-a2} \\
%   & & \hspace*{0.5in} \neg\underE{\committed(\C{Wd1})} \conj
%       (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
    & & \hspace*{0.8in}\Rightarrow \C{B=k-a2} \conj 
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in} \conj \underE{\committed(\C{Wd1})} \conj
        (\E'-\E) \Vdash {\committed(\C{Wd2})}\\
%       \C{COMMIT(Wd2)} \in (\E'.\A-\E.\A) \\
    & & \hspace*{0.6in}\Rightarrow \C{B=k-a1-a2} \conj
        \E' \Vdash \C{Wd2} \wrstoar \C{B} \\
    & & \hspace*{0.37in}\conj \forall(\eta \in \E'.\A - 
        \E.\A).~\txn(\eta) = \C{Wd2}\}\\
\end{array}
\end{smathpar}
For the sake of completeness, we also explicitly represent the fact
that all the effects added by $R_1$ are of \C{Wd2}. This is needed to
prove that an interference from \C{Wd2} does not affect the local
state of \C{Wd1}. $R_1$ refers to labels (\C{Wd1} and \C{Wd2}) of both
the transactions. This is allowed because labels are artifacts of the
execution $\E$; they are not (local) variables.
